Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2019-03-22 area_agg_seq_tsas.tex
added discussion about DAGs; several improvements

\author{Dongliang Peng}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{0000-0001-6848-3545}
\affiliation{%
  \institution{Chair of Computer Science I, 
  	University of W\"urzburg}
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin}
%  \state{Ohio}
%  \postcode{43017-6221}
  \country{Germany}
}
\email{dongliang.peng@uni-wuerzburg.de}

@@

\begin{abstract}
To provide users with maps of different scales and 
to allow them to zoom in and out without losing context,
automatic methods for map generalization are needed.
We approach this problem for land-cover maps.
Given two land-cover maps at two different scales, 
we want to find a sequence of small incremental
changes that gradually transforms one map into the other.
We assume that the two input maps consist of polygons 
each of which belongs to a given land-cover class. 
Every polygon on the smaller-scale map
is the union of a set of adjacent polygons 
on the larger-scale map.

@@

We assume that there exist many-to-one relationships between the 
areas of the
start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
that aggregate land-cover areas
result in many-to-one relationships.
Their inputs and generalized results together
can be used as our inputs.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its 
components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce land-cover maps at intermediate scales.

In this paper, we try to find an optimal sequence
to aggregate the land-cover areas on the start map
one by one until we arrive the goal map.
We first independently deal with each region of the goal map 
(with its components on the start map).
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence,
which transforms the start map into the goal map. 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.

\mypar{Contribution}
We formally define our problem, 
introduce the basic concepts of our method, 
and analyze the size of our model in a worst-case scenario
(\sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions in 
\sect\ref{sec:AreaAgg_CostFunctions}.
We prove that our problem is NP-hard
(\sect\ref{sec:AreaAgg_NP-hardness}).
Then, we develop and compare three methods 
for finding aggregation sequences.
First, we present 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we develop a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and then we solve this program with minimizing our cost function.
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether it is worth 
to use \Astar or the ILP-based algorithm, 
which are more complex and slower.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the conclusions, we show possible ways to improve our 
methods in \sect\ref{sec:AreaAgg_Conclusions}.

@@

\section{Related Work}

@@

We show how to compute an aggregation sequence 
for a single region, $R$. 
For a goal map with many regions,
we ``interleave'' the sequences for each of them
with respect to the order of the smallest patches 
(see for example \fig\ref{fig:AreaAgg_IntegrateSequence}).
This integration is similar to the merge step in the 
Mergesort algorithm; 
see \textcite[pp.~29--37]{Cormen2009}.
To allow us to describe our method more easily,
below we assume that the goal map has only one region.
This region consists of~$n$ land-cover 
areas (components) on the start map. 
In other words, the union of the~$n$ land-cover areas 
is the only region on the goal map.
\begin{figure*}[tb]
\centering
\includegraphics[page=2]{AreaAgg_Preliminaries}
\caption{Integrating two aggregation sequences 
	of different regions: 
	the resulting sequence contains the given sequences 
	as subsequences and 
	always takes the subdivision with smallest patch next.
	The gray arrows show the integration of the two regions.
}
\label{fig:AreaAgg_IntegrateSequence}
\end{figure*}

@@

\mypar{Model}
We consider a directed graph $G_\mathrm{S}$, 
which we call the \emph{subdivision graph} 
(see \fig\ref{fig:AreaAgg_SubdivisionName}). 
The node set $V_\mathrm{S}$ of~$G_\mathrm{S}$ 
contains a node for every
possible map (or \emph{subdivision}), including the start map, 
all possible intermediate-scale maps, and the goal map.
The arc set~$E_\mathrm{S}$ of~$G_\mathrm{S}$ 
contains an arc $(\Pnode, P_{t+1,j})$ 
between any two maps~$\Pnode$ and~$P_{t+1,j}$ in~$V_\mathrm{S}$ 
if~$P_{t+1,j}$ can be reached from~$\Pnode$ 
with a single aggregation operation,
involving a smallest area.
Then, any directed path in~$G_\mathrm{S}$ 
from the start map to the goal map
defines a possible aggregation sequence.
Our idea is to obtain an optimal aggregation sequence through 
computing a minimum-weight path from the start to the goal.
This idea obviously requires that the arc weights are 
set such that a minimum-weight start--goal
path does actually correspond to an aggregation sequence of 
maximum cartographic quality.  
Moreover, putting the idea to practice is far from trivial 
since graph~$G_\mathrm{S}$ can be huge as we will argue later.
We compare a greedy algorithm, \Astar, and an ILP-based algorithm
in finding such paths.
Note that we only know 
subdivisions~$\Pstart$ and~$\Pgoal$ at the beginning.
We generate a subdivision (node) only when we want to visit it.

@@

@@

\mypar{Exponential lower bound}
We now analyze the size of subdivision graph~$G_\mathrm{S}$.
Our analysis is inspired by \textcite{Keane1975Size},
where we also use a row of~$n$~areas.
In our instance
(see \fig\ref{fig:AreaAgg_ExponentialSize}), 
the start map consists of~$n=2k+1$ rectangles,
and the goal map is simply the union of the~$n$ rectangles.
At layer~$L_{k+1}$, we need to remove~$k$ of the~$2k$ 
intermediate vertical boundaries. 
For this, the number of choices is~$
\binom{2k}{k}
= \frac{2k\cdot (2k-1)\cdot \ldots \cdot (k+1)}
{k\cdot (k-1)\cdot \ldots \cdot 1}
\ge 2^k = 2^{(n-1)/2}$.
That is to say, the size of our model
has an exponential lower bound.

@@

Although we have shown that the graph of subdivisions
has an exponential size
(see \sect\ref{sec:AreaAgg_Preliminaries}),
one may develop a clever algorithm 
to find an optimal sequence efficiently.
In the following, we prove that 
finding such a sequence is indeed NP-hard.
In the proof, we neglect the cost of compactness or the cost of length.
Considering one of the two costs 
will make the finding even more difficult.

@@

\begin{proof}
Our NP-hardness proof is by reduction from 
the NP-complete problem \textsc{PlanarVertexCover}, 
which is to decide, for a given 
planar graph~$G_\mathrm{A} = (V_\mathrm{A},E_\mathrm{A})$, 
whether there exists a vertex cover 
with at most a given number~$k_\mathrm{A}$ of vertices. 
For an instance of \textsc{PlanarVertexCover}
(\fig\ref{fig:AreaAgg_Reduction}a), 
we define a corresponding instance of \textsc{AreaAggregationSequence}
whose start map consists of gray, black, and white areas and 
whose goal map consists of only one large gray patch.
The adjacency graphs of the two maps are illustrated 
in \figs\ref{fig:AreaAgg_Reduction}b and~\ref{fig:AreaAgg_Reduction}c, 
where the colors of the vertices represent 
the colors of the corresponding areas.
More precisely, for each vertex of~$G_\mathrm{A}$
in \fig\ref{fig:AreaAgg_Reduction}a, 
we define a gray vertex and a black vertex, 
which we connect with an edge. 
For each edge of~$G_\mathrm{A}$, 
we define two white vertices and 
connect them with the two black vertices
(\fig\ref{fig:AreaAgg_Reduction}b).

@@

We define the weights of the vertices 
in \fig\ref{fig:AreaAgg_Reduction}b as follows:
\begin{itemize}
\item Every white vertex has weight~$1$.
\item Every black vertex has weight~$2$.
\item Every gray vertex has weight~$2|V_\mathrm{A}| + 2|E_\mathrm{A}|$,
which is equal to the total weight of all white and black vertices.
\end{itemize}
Since in each aggregation step, 
we require the smallest area to be aggregated with one of its neighbors, 
our definition of the weights to a certain degree determines 
the order in which the vertices are selected:
\begin{itemize}
\item \emph{Phase I}: In each of the first~$2|E_\mathrm{A}|$ steps, 
a white vertex is selected and merged with one of its neighbors, 
such that the white vertex receives the neighbor's color or vice versa.
\item \emph{Phase II}: In each of the next~$|V_\mathrm{A}|$ steps, 
a non-gray vertex is selected and merged with one of its neighbors.
\item \emph{Phase III}: $|V_\mathrm{A}|-1$ steps remain to reach the goal map.
\end{itemize}

To complete the reduction, 
we need to define the costs of color changes. 
For any color change, 
we charge one unit of cost per unit weight.
Due to our construction, Phases II and III can be accomplished with
a total cost of~$2|V_\mathrm{A}|+2|E_\mathrm{A}|$, 
no matter how Phase I is accomplished.
This is because, after Phase I, 
every non-gray patch will be adjacent to a gray patch (vertex).
Thus, if any non-gray patch becomes selected in Phase II, 
it can aggregate with a gray patch (vertex) and 
receive the color gray. 
This implies that Phase II costs $2|V_\mathrm{A}|+2|E_\mathrm{A}|$ 
(which is equal to the total weight of 
all initially white and black vertices) and, 
since after Phase II all patches are gray, 
Phase III does not cause any additional cost.  
It is also clear that 
there is no cheaper way to accomplish Phases II and III,
since it is impossible to color a vertex gray in Phase I.
Consequently, since the total cost of Phases II and III is fixed, 
it is only interesting to ask 
at which cost Phase I can be accomplished.
It turns out that, if $G_\mathrm{A}$ 
has a vertex cover $C_\mathrm{A} \subseteq V_\mathrm{A}$, 
then Phase I can be accomplished with cost $2|C_\mathrm{A}|$;
only the black vertices corresponding to vertices in~$C_\mathrm{A}$ 
need to change their color from black to white, and 
each of them has weight~$2$ (see \fig\ref{fig:reduction2}).
To summarize, if graph~$G_\mathrm{A}$ has a vertex cover~$C_\mathrm{A}$, 
then the corresponding instance of \textsc{AreaAggregationSequence} 
has a solution of 
total cost~$2|C_\mathrm{A}|+2|V_\mathrm{A}|+2|E_\mathrm{A}|$.

@@

\sect\ref{sec:AreaAgg_Preliminaries} has shown that
the size of finding an optimal aggregation sequence 
can be exponential.
That is to say, the graph~$G_\mathrm{S}$---our search space---can 
be of exponential size.
In order to avoid computing the whole graph explicitly,
we use the \Astar algorithm \parencite{Hart1968,PatelAStar}.
To save time and memory, 
we generate a subdivision, \Pnode, only 
when we are going to visit it.
\Astar uses a clever best-first search 
to find a shortest path 
from subdivision~$\Pstart$ to subdivision~$\Pgoal$.  
For \Pnode,
\Astar considers the exact cost of a shortest path 
from~\Pstart to~\Pnode 
and estimates the cost to get from~\Pnode to~\Pgoal. 
\Astar explores the nodes earlier 
if they are estimated to be closer to the goal.
\Astar can be seen as a refinement of Dijkstra's algorithm
\parencite{Dijkstra1959}.

@@

From subdivision~\Pnode to subdivision~$P_{t+1,i''_{t+1}}$,
we get a new patch because of the aggregation.
The new patch is certainly less compact than a regular polygon 
with~$\mathcal{N}_{t+1,i''_{t+1}}$ edges.
In order to estimate the compactness of the new patch, 
we assume that 
the new patch has the shape of a regular polygon 
with~$\mathcal{N}_{t+1,i''_{t+1}}$ edges 
(see \eq\ref{eq:LeftEdgeNum}).
A regular polygon with~$\mathcal{N}$ edges has compactness
\begin{equation*}
\label{eq:comp_regular}
c_\mathrm{reg}(\mathcal{N})=
\sqrt{\frac{\pi}{\mathcal{N}} \bigg/
	\tan{\frac{\pi}{\mathcal{N}}}}.
\end{equation*}
Note that~$c_\mathrm{reg}(\mathcal{N})$ increases 
with increasing~$\mathcal{N}$.
A patch with~$\mathcal{N}_{t+1,i''_{t+1}}$ edges has
compactness~$c_\mathrm{reg} (\mathcal{N}_{t+1,i''_{t+1}})$.
According to our previous assumption, 
at each step we are always able to aggregate the two patches 
that are the least compact in the subdivision.
We denote the compactness values of the two patches
by~$c_\mathrm{min1}(\Pnode)$ and~$c_\mathrm{min2}(\Pnode)$.
Recall that we use~$C(\Pnode)$ to denote 
the set of compactness values of the patches
in subdivision~$\Pnode$ 
(see \sect\ref{sec:AreaAgg_f_comp}).
Then the set of compactness values 
for subdivision~$P_{t+1,i''_{t+1}}$ is 
\begin{equation}
\label{eq:compsetnew}
C(P_{t+1,i''_{t+1}})=
C(\Psnode)\cup 
\{c_\mathrm{reg} (\mathcal{N}_{t+1,i''_{t+1}})\}
\setminus \{c_\mathrm{min1}(\Pnode), c_\mathrm{min2}(\Pnode)\}.
\nonumber
\end{equation}
We compute the estimated average compactness 
by calculating the average 
of the values in set~$C(P_{t+1,i''_{t+1}})$.
Finally, we compute the estimated cost of compactness 
for subdivision~$P_{t+1,i''_{t+1}}$ by \eq\ref{eq:f_comp}.

@@

>>>>

\author{Dongliang Peng}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{0000-0001-6848-3545}
\affiliation{%
  \institution{Chair of Computer Science I, 
  	University of W\"urzburg}
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin}
%  \state{Ohio}
%  \postcode{43017-6221}
  \country{Germany}
}
\email{www1.informatik.uni-wuerzburg.de/peng}

@@

\begin{abstract}
To provide users with maps of different scales and 
to allow them to zoom in and out without losing context,
automatic methods for map generalization are needed.
We approach this problem for land-cover maps.
Given two land-cover maps at two different scales, 
we want to find a sequence of small incremental
changes that gradually transforms one map into the other.
We assume that the two input maps consist of polygons 
each of which belongs to a given land-cover type. 
Every polygon on the smaller-scale map
is the union of a set of adjacent polygons 
on the larger-scale map.

@@

We assume that there exist many-to-one relationships 
between the areas of the start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
result in many-to-one relationships
when aggregating land-cover areas.
Their inputs and generalized results together
can be used as our inputs.
However, we should not use those algorithms
to generate a sequence of maps at different scales, 
because those algorithms do not take into account 
the consistence of the generated maps.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce a sequence land-cover maps.

In this paper, we try to find an optimal sequence
to aggregate the land-cover areas on the start map
one by one until we arrive the goal map.
We first independently deal with each region of the goal map 
(with its components on the start map).
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence,
which transforms the start map into the goal map
(see \fig\ref{fig:AreaAgg_IntegrateSequence}). 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.

\begin{figure*}[tb]
\centering
\includegraphics[page=2]{AreaAgg_Preliminaries}
\caption{Integrating two aggregation sequences 
	of different regions: 
	the resulting sequence contains the given sequences 
	as subsequences and 
	always takes the subdivision with smallest patch next.
	The gray arrows show the integration of the two regions.
}
\label{fig:AreaAgg_IntegrateSequence}
\end{figure*}

\mypar{Contribution}
We show related work (\sect\ref{sec:AreaAgg_RelatedWork}).
Then, we formally model our problem, 
analyze the size of our model in a worst-case scenario,
introduce our methods,
and present the basic concepts of our method
(\sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions 
(\sect\ref{sec:AreaAgg_CostFunctions}).
We prove that our problem is NP-hard
(\sect\ref{sec:AreaAgg_NP-hardness}).
Then, we develop and compare three methods 
for finding aggregation sequences.
First, we present 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we develop a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and we solve this ILP with minimizing our cost function
(\sect\ref{sec:AreaAgg_ILP}).
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether it is worth 
to use \Astar or the ILP-based algorithm, 
which are more complex and slower.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the conclusions, we show possible ways to improve our 
methods (\sect\ref{sec:AreaAgg_Conclusions}).

@@

\section{Related Work}
\label{sec:AreaAgg_RelatedWork}

@@

We show how to compute an aggregation sequence 
for a single region, $R$. 
For a goal map with many regions,
we ``interleave'' the sequences for each of them
with respect to the order of the smallest patches 
(see for example \fig\ref{fig:AreaAgg_IntegrateSequence}).
This integration is similar to the merge step in the 
Mergesort algorithm; 
see \textcite[pp.~29--37]{Cormen2009}.
To allow us to describe our method more easily,
below we assume that the goal map has only one region.
This region consists of~$n$ land-cover 
areas (components) on the start map. 
In other words, the union of the~$n$ land-cover areas 
is the only region on the goal map.

@@

\mypar{Model}
We consider a directed graph $G_\mathrm{S}$, 
which we call the \emph{subdivision graph} 
(see \fig\ref{fig:AreaAgg_SubdivisionName}). 
The node set $V_\mathrm{S}$ of~$G_\mathrm{S}$ 
contains nodes for all the
possible maps (or \emph{subdivisions}), including the start map, 
all possible intermediate-scale maps, and the goal map.
The arc set~$E_\mathrm{S}$ of~$G_\mathrm{S}$ 
contains an arc $(\Pnode, P_{t+1,j})$ 
between any two maps~$\Pnode$ and~$P_{t+1,j}$ in~$V_\mathrm{S}$ 
if~$P_{t+1,j}$ can be reached from~$\Pnode$ 
with a single aggregation operation,
involving a smallest area.
On this basis, any directed path in~$G_\mathrm{S}$ 
from the start map to the goal map
defines a possible aggregation sequence.

@@

\mypar{Exponential lower bound}
We now analyze the size of subdivision graph~$G_\mathrm{S}$.
Our analysis is inspired by \textcite{Keane1975Size},
where we use a row of~$n$ land-cover areas.
In our instance
(see \fig\ref{fig:AreaAgg_ExponentialSize}), 
the start map consists of~$n=2k+1$ rectangles,
and the goal map is simply the union of the~$n$ rectangles.
At layer~$L_{k+1}$, we need to remove~$k$ of the~$2k$ 
intermediate vertical boundaries. 
For this, the number of choices is~$
\binom{2k}{k}
= \frac{2k\cdot (2k-1)\cdot \ldots \cdot (k+1)}
{k\cdot (k-1)\cdot \ldots \cdot 1}
\ge 2^k = 2^{(n-1)/2}$.
That is to say, the size of our model
has exponential lower bound.

\mypar{Methods}
Our idea is to obtain an optimal aggregation sequence through 
computing a minimum-weight path from the start to the goal 
(see \fig\ref{fig:AreaAgg_SubdivisionName}).
This idea obviously requires that the arc weights are 
set such that a minimum-weight start--goal
path does actually correspond to an aggregation sequence of 
maximum cartographic quality.  
Moreover, putting the idea to practice is far from trivial 
since graph~$G_\mathrm{S}$ can be huge.
We compare a greedy algorithm, \Astar, and an ILP-based algorithm
in finding such paths.
Note that our inputs are only
subdivisions~$\Pstart$ and~$\Pgoal$.
We generate a subdivision (node) only when we want to visit it.

In directed acyclic graphs, shortest paths can be found slightly faster 
than in general directed or undirected graphs.
An off-the-shelf shortest-path algorithm for directed acyclic graphs,
however, will explore the whole graph, which has exponential size.
The challenge in our work was to tune the A* algorithm such that it
explores only a small fraction of the graph.

@@

@@

Although we have shown that the graph of subdivisions
has an exponential size
(see \sect\ref{sec:AreaAgg_Preliminaries}),
one may develop a clever algorithm 
to find an optimal sequence efficiently.
In the following, we prove that 
finding such a sequence is indeed NP-hard.
In the proof, we neglect the cost of compactness or the cost of length.
Considering one of the two costs 
will make the computation even more difficult.

@@

\begin{proof}
Our NP-hardness proof is by reduction from 
the NP-complete problem \textsc{PlanarVertexCover}, 
which is to decide, for a given 
planar graph~$G_\mathrm{A} = (V_\mathrm{A},E_\mathrm{A})$, 
whether there exists a vertex cover 
with at most a given number~$k_\mathrm{A}$ of vertices. 
For an instance of \textsc{PlanarVertexCover}
(\fig\ref{fig:AreaAgg_Reduction}a), 
we define a corresponding instance of \textsc{AreaAggregationSequence}
whose start map consists of gray, black, and white areas and 
whose goal map consists of only one large gray patch.
The adjacency graphs of the two maps are illustrated 
in \figs\ref{fig:AreaAgg_Reduction}b and~\ref{fig:AreaAgg_Reduction}c, 
where the colors of the vertices represent 
the colors of the corresponding areas.
More precisely, for each vertex of~$G_\mathrm{A}$
in \fig\ref{fig:AreaAgg_Reduction}a, 
we define a gray vertex and a black vertex, 
which we connect with an edge. 
For each edge $\{u,v\}$ of~$G_\mathrm{A}$, 
we define two white vertices and 
connect each of them both with the black vertex for $u$
and the black vertex for $v$
(\fig\ref{fig:AreaAgg_Reduction}b).

@@

We define the weights of the vertices 
in \fig\ref{fig:AreaAgg_Reduction}b as follows:
\begin{itemize}
\item Every white vertex has weight~$1$.
\item Every black vertex has weight~$2$.
\item Every gray vertex has weight~$2|V_\mathrm{A}| + 2|E_\mathrm{A}|$,
which is equal to the total weight of all white and black vertices.
\end{itemize}
When we merge two vertices, 
the weight of the new vertex is the sum of the two.
In each aggregation step, 
we require the smallest area to be aggregated with one of its neighbors.
The area sizes correspond to the weights of the vertices in \fig\ref{fig:AreaAgg_Reduction}b.   
Therefore, our definition of the weights to a certain degree determines 
the order in which the vertices are selected:
\begin{itemize}
\item \emph{Phase I}: In each of the first~$2|E_\mathrm{A}|$ steps, 
a white vertex is selected and merged with one of its neighbors, 
such that the white vertex receives the neighbor's color or vice versa
(\fig\ref{fig:reduction2} shows a possible result).
\item \emph{Phase II}: In each of the next~$|V_\mathrm{A}|$ steps, 
a non-gray vertex is selected and merged with one of its neighbors.
\item \emph{Phase III}: $|V_\mathrm{A}|-1$ steps remain to reach the goal map.
\end{itemize}

To complete the reduction, 
we need to define the costs of color changes. 
For any color change, 
we charge one unit of cost per unit weight.
Due to our construction, Phases II and III can be accomplished with
a total cost of~$2|V_\mathrm{A}|+2|E_\mathrm{A}|$, 
no matter how Phase I is accomplished.
This is because, after Phase I, 
every non-gray patch will be adjacent to a gray patch (vertex).
Thus, if any non-gray patch becomes selected in Phase II, 
it can be aggregated with a gray patch (vertex) and 
receive the color gray. 
This implies that Phase II costs $2|V_\mathrm{A}|+2|E_\mathrm{A}|$ 
(which is equal to the total weight of 
all initially white and black vertices) and, 
since after Phase II all patches are gray, 
Phase III does not cause any additional cost.  
It is also clear that 
there is no cheaper way to accomplish Phases II and III,
since it is impossible to color a vertex gray in Phase I.
Consequently, since the total cost of Phases II and III is fixed, 
it is only interesting to ask 
at which cost Phase I can be accomplished.
It turns out that, if $G_\mathrm{A}$ 
has a vertex cover $C_\mathrm{A} \subseteq V_\mathrm{A}$, 
then Phase I can be accomplished with cost $2|C_\mathrm{A}|$;
only the black vertices corresponding to vertices in~$C_\mathrm{A}$ 
need to change their color from black to white, and 
each of them has weight~$2$ (see \fig\ref{fig:reduction2}).
To summarize, if graph~$G_\mathrm{A}$ has a vertex cover~$C_\mathrm{A}$, 
then the corresponding instance of \textsc{AreaAggregationSequence} 
has a solution of 
total cost~$2|C_\mathrm{A}|+2|V_\mathrm{A}|+2|E_\mathrm{A}|$.

@@

\sect\ref{sec:AreaAgg_Preliminaries} has shown that
the size of finding an optimal aggregation sequence 
can be exponential.
That is to say, the graph~$G_\mathrm{S}$---our search space---can 
be of exponential size.
In order to avoid computing the whole graph explicitly,
we use the \Astar algorithm \parencite{Hart1968,PatelAStar}.
To save time and memory, 
we generate a subdivision, \Pnode, only 
when we are going to visit it.
The \Astar algorithm uses a clever best-first search 
to find a shortest path 
from subdivision~$\Pstart$ to subdivision~$\Pgoal$.  
For \Pnode,
\Astar considers the exact cost of a shortest path 
from~\Pstart to~\Pnode 
and estimates the cost to get from~\Pnode to~\Pgoal. 
The \Astar algorithm explores the nodes earlier 
if they are estimated to be closer to the goal.
The \Astar algorithm can be seen as a refinement of Dijkstra's algorithm
\parencite{Dijkstra1959}.

@@

From subdivision~\Pnode to subdivision~$P_{t+1,i''_{t+1}}$,
we get a new patch because of the aggregation.
The new patch is certainly less compact than a regular polygon 
with~$\mathcal{N}_{t+1,i''_{t+1}}$ edges.
In order to estimate the compactness of the new patch, 
we assume that 
the new patch has the shape of a regular polygon 
with~$\mathcal{N}_{t+1,i''_{t+1}}$ edges 
(see \eq\ref{eq:LeftEdgeNum}).
A regular polygon with~$\mathcal{N}$ edges has compactness
\begin{equation*}
\label{eq:comp_regular}
c_\mathrm{reg}(\mathcal{N})=
\sqrt{\frac{\pi}{\mathcal{N}} \bigg/
	\tan{\frac{\pi}{\mathcal{N}}}}.
\end{equation*}
Note that compactness~$c_\mathrm{reg}(\mathcal{N})$ increases 
with increasing~$\mathcal{N}$.
A patch with~$\mathcal{N}_{t+1,i''_{t+1}}$ edges has
compactness~$c_\mathrm{reg} (\mathcal{N}_{t+1,i''_{t+1}})$.
According to our previous assumption, 
at each step we are always able to aggregate the two patches 
that are the least compact in the subdivision.
We denote the compactness values of the two patches
by~$c_\mathrm{min1}(\Pnode)$ and~$c_\mathrm{min2}(\Pnode)$.
Recall that we use~$C(\Pnode)$ to denote 
the set of compactness values of the patches
in subdivision~$\Pnode$ 
(see \sect\ref{sec:AreaAgg_f_comp}).
Then the set of compactness values 
for subdivision~$P_{t+1,i''_{t+1}}$ is 
\begin{equation}
\label{eq:compsetnew}
C(P_{t+1,i''_{t+1}})=
C(\Psnode)\cup 
\{c_\mathrm{reg} (\mathcal{N}_{t+1,i''_{t+1}})\}
\setminus \{c_\mathrm{min1}(\Pnode), c_\mathrm{min2}(\Pnode)\}.
\nonumber
\end{equation}
We compute the estimated average compactness 
by calculating the average 
of the values in set~$C(P_{t+1,i''_{t+1}})$.
Finally, we compute the estimated cost of compactness 
for subdivision~$P_{t+1,i''_{t+1}}$ by \eq\ref{eq:f_comp}.

@@

We want to compare the \Astar algorithm with 
integer linear programming in finding 
optimal sequences for our aggregation problem. 
Since integer linear programming
can handle only linear constraints, 
we define the compactness of a subdivision as 
the length of the subdivision's interior boundaries.
That is, we use cost function~$g_2$ (see \eq\ref{eq:g_2}).
Our basic idea is to formalize the problem of 
finding a shortest path as an ILP.
Then we solve this ILP by minimizing the total cost.
As the \Astar algorithm performed better in our case study,
here we skip the formulation of our ILP.
The formulation can be found in Appendix~\ref{app:AreaAgg_ILP}.

\appendix
\section{Formulation of Integer Linear Programming}
\label{app:AreaAgg_ILP}
